---
title: "Automated checks of manual extractions"
author: "ses"
date: "5/14/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Setup


```{r global-knitr-options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H',
  fig.asp = 0.618,
  fig.width = 5,
  fig.cap = "", 
  fig.path = "",
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  fig.show = "hold")
```


## Load packages

```{r ipsum_setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}

library(tidyverse)  # data wrangling
library(rvest)  # web scraping
library(xml2)  # web scraping

library(printr)  # print dfs as tables
library(glue)  # glueing
library(rcrossref)  # citation count
#library(conflicted)  # detect package confligcs
library(readxl)  # import excel data
library(janitor)  # clean data 
library(here)  # relative file paths
library(writexl)  # write to xslx
#library(polite)  # polite scraping
library(testthat)  # testing
library(tools)  # testing/error messages

```




Declare conflict preferences:

```{r}
#conflict_prefer("filter", "dplyr")
```





## Source functions

```{r}
source("funs/helper-funs.R")
source("funs/funs-parse-cochrane.R")
source("funs/get_summary_table.R")
source("funs/parse-review-parts.R")
```



## Some constants


### dois

```{r}
sample_doi <- "14651858.CD001180.pub4"

sample_doi2 <- "14651858.CD011923.pub2"
# https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD011923.pub2/full#CD011923-sec1-0001
# 
sample_doi3 <- "14651858.CD004123.pub4"
```



### Paths

```{r}
output_path <- paste0(here(),"/output/comparison/nk")
```




# Prepare MANUALLY (by human) extracted data

## Import manually extracted data

### ss



## Prep

Define here the (short) name of the reviewer.

```{r}
reviewer_selected <- "np"
```


```{r}
extractions_manual_path <- glue("manual-extractions/{reviewer_selected}/InEffective Cochrane Reviews Final_{reviewer_selected}.xlsx")
```

This is the relative path the file with the manually extracted Cochrane data:

```{r}
cat(extractions_manual_path)
```


Check if file exists:

```{r}
if (!file.exists(extractions_manual_path)) stop("File not found!") else message("File found.")
```



```{r}
extractions_manual <-
  read_xlsx(path = extractions_manual_path,
            skip = 1) %>%   # invalid header row
  slice(-c(1,2))  %>% # invalued header rows
  rename(reviewer = `...1`)

```


## Clean the cols

```{r}
extractions_manual2 <-
  extractions_manual %>% 
  clean_names()
```


### Rename cols

```{r}
extractions_manual3 <-
  extractions_manual2

names(extractions_manual3)[3] <- "SoF_table_number"
names(extractions_manual3)[4] <- "is_outdated"
names(extractions_manual3)[5] <- "is_withdrawn"
names(extractions_manual3)[7] <- "GRADE_used"
names(extractions_manual3)[22] <- "first_high_qual_outcome"
```


### Recode 

```{r}
extractions_manual3a <-
  extractions_manual3 %>% 
  mutate(across(.cols = c(3:7),
                .fns = tolower)) %>% 
  mutate(is_outdated = ifelse(is_outdated == "yes", TRUE, FALSE),
         is_withdrawn = ifelse(is_withdrawn == "yes", TRUE, FALSE),
         GRADE_used = ifelse(GRADE_used == "yes", TRUE, FALSE)) %>% 
  group_by(url) %>% 
  mutate(SoF_table_number = row_number()) %>% 
  ungroup() %>% 
  mutate(has_high_quality_outcome = ifelse(
    str_count(str_squish(first_high_qual_outcome)) > 0, TRUE, FALSE)) %>% 
  mutate(has_high_quality_outcome = replace_na(has_high_quality_outcome, FALSE)) %>% 
  mutate(first_high_qual_outcome = replace_na(first_high_qual_outcome, "no high quality outcome"))
```



Checks

```{r}
extractions_manual3a %>% 
  count(GRADE_used)
```


```{r}
extractions_manual3a %>% 
  count(has_high_quality_outcome)
```





### Sanitize url


```{r}
extractions_manual3b <- 
extractions_manual3a %>% 
  mutate(cochrane_id = sanitize_review_url(url))
```



## Select columns 


### Cols to be checked by the algorithm 


```{r}
cols_to_be_checked <-
  c("is_outdated",
    "is_withdrawn",   
    "GRADE_used",
    "first_high_qual_outcome",
    "has_high_quality_outcome"
    )
```


### ID columns


```{r}
id_cols_manual <-
  c("reviewer", "title", "cochrane_id", "SoF_table_number")
```




## Select relevant columns


```{r}
extractions_manual4 <-
  extractions_manual3b %>% 
  select(any_of(c(id_cols_manual, cols_to_be_checked)))
```


```{r}
names(extractions_manual4)
```



## Filter relevant rows


```{r}
extractions_manual5 <-
  extractions_manual4 %>% 
  filter(tolower(reviewer) == reviewer_selected)
```




## Checks

```{r}
# extractions_manual5 %>% 
#   filter(cochrane_id == sample_doi3) %>% 
#   select(SoF_table_number, GRADE_used)
```


```{r}
extractions_manual5 %>% 
  count(first_high_qual_outcome)
```



# Prepare MACHINE extracted data

## Import machine extracted data


```{r}
extractions_machine_path <- glue( "output/{reviewer_selected}/reviews_output_machine_{reviewer_selected}.xlsx")
```

This is the name of the file with the machine extracted data:

```{r}
extractions_machine_path
```


Check if this file exists:

```{r}
if (!file.exists(extractions_machine_path)) stop("File does not exist!") else message("File found.")
```


```{r}
extractions_machine <- 
  read_xlsx(extractions_machine_path)
```

```{r}
glimpse(extractions_machine)
```

```{r}
extractions_machine %>% 
  count(SoF_table_number)
```


## Some preparations


```{r}
extractions_machine2 <-
  extractions_machine %>% 
  mutate(is_outdated = !is_most_recent_version,
         url = doi,
         cochrane_id = sanitize_review_url(doi)) 
```


### Add `GRADE_used`


`GRADE_used` is set to TRUE if GRADE was used for at least one measure in the respective SOF.

Check

```{r}
# extractions_machine2 %>% 
#   filter(cochrane_id == sample_doi3) %>% 
#     select(GRADE, title)
```



```{r}
extractions_machine3 <-
  extractions_machine2 %>% 
  group_by(doi, SoF_table_number) %>% 
  mutate(GRADE_used = str_detect(GRADE, "⊕|⊝")) %>% 
  mutate(GRADE_used = ifelse(is.na(GRADE_used), FALSE, TRUE )) %>% 
  mutate(GRADE_used = ifelse(any(GRADE_used == TRUE), TRUE, FALSE)) %>% 
  ungroup() %>% 
  mutate(has_high_quality_outcome = str_detect(tolower(GRADE), "high")) %>% 
  mutate(has_high_quality_outcome = ifelse(
    is.na(has_high_quality_outcome), FALSE, has_high_quality_outcome)) %>% 
  mutate(first_high_qual_outcome = 
           ifelse(has_high_quality_outcome == TRUE,
                  Outcomes, "no high quality outcome")) %>% 
  ungroup()
  
```

**NOTE**. Although the column `first_high_qual_outcome` suggests via its name that only the *first* high quality outcome is reported, this column checks whether the respective measure of th SoF table is of high GRADE level or not.


### Check column type

`SoF_table_number` should be of type `integer`:

```{r}
extractions_machine3a <-
  extractions_machine3 %>% 
  mutate(SoF_table_number = parse_number(SoF_table_number))
```


```{r}
extractions_machine3a %>% 
  select(SoF_table_number) %>% 
  str()
```


### Checks

```{r}
extractions_machine3a %>% 
  count(has_high_quality_outcome)
```


```{r}
extractions_machine3a %>% 
  count(first_high_qual_outcome)
```



```{r}
# extractions_machine3 %>% 
#   filter(cochrane_id == sample_doi3) %>% 
#   select(SoF_table_number, GRADE_used)
```


## Select relevant columns


```{r}
extractions_machine4 <-
  extractions_machine3a %>% 
  select(cochrane_id, SoF_table_number,
         any_of(cols_to_be_checked))
```


```{r}
names(extractions_machine4)
```



# Merge manual and machine extracted data


## Check 1 

Are the ID (sample dois) correctly parsed?

```{r}
# extractions_machine4 %>% 
#   filter(cochrane_id == sample_doi) %>% 
#   pull(cochrane_id)
# 
# 
# extractions_manual5 %>%
#   filter(cochrane_id == sample_doi) %>% 
#   pull(cochrane_id)
```


## Check 2


Are the `GRADE_used` cols are correctly parsed?


```{r}
# extractions_machine4 %>% 
#   filter(cochrane_id == sample_doi2) %>% 
#   select(SoF_table_number, GRADE_used)
```


```{r}
# extractions_manual5 %>% 
#   filter(cochrane_id == sample_doi2) %>% 
#   select(SoF_table_number, GRADE_used)
```




## Merge em!


```{r}
extractions_merged <- 
  extractions_manual5 %>% 
  left_join(y = extractions_machine4, 
            by = c("cochrane_id", "SoF_table_number"))
```


- x: manual (reviewer)
- y: machine 


```{r}
names(extractions_merged)
```


# Check for differences between manual and machine extractions


```{r}
extractions_merged2 <-
  extractions_merged %>% 
  mutate(identical_outdated = is_outdated.x == is_outdated.y,
         identical_withdrawn = is_withdrawn.x == is_withdrawn.y,
         identical_GRADE_used = GRADE_used.x == GRADE_used.y) %>% 
  mutate(identical_has_high_quality_outcome = 
           identical(has_high_quality_outcome.x, has_high_quality_outcome.y)) %>% 
  mutate(identical_first_high_qual_outcome = 
           case_when(
             identical(first_high_qual_outcome.x, first_high_qual_outcome.y) ~ TRUE,
             str_detect(first_high_qual_outcome.x, first_high_qual_outcome.y) ~ TRUE,
             str_detect(first_high_qual_outcome.y, first_high_qual_outcome.x) ~ TRUE,
             TRUE ~ FALSE
           ))
```



## Checks

```{r}
extractions_merged2 %>% 
  count(identical_first_high_qual_outcome)
```


```{r}
extractions_merged2 %>% 
  count(identical_has_high_quality_outcome)
```


## Filter for differences

A difference is indicative for some error, either by the machine or by the reviewer. To be inspected with closer scrunity.


```{r}
extractions_merged3 <-
  extractions_merged2 %>% 
  filter(identical_outdated == FALSE |
         identical_withdrawn == FALSE |
         identical_GRADE_used == FALSE |
        identical_has_high_quality_outcome == FALSE |
          identical_has_high_quality_outcome == FALSE)

extractions_merged
```



## Write to disk


```{r}
write_xlsx(extractions_merged2,
           path = paste0(output_path, "/comparison_human_machine_ss" , ".xlsx"))


write_xlsx(extractions_merged3,
           path = paste0(output_path, "/comparison_human_machine_problems_only_ss.xlsx"))
```

