---
title: "01-Cochrane-Scraping"
output: 
  hrbrthemes::ipsum:
    toc: true
    number_section: TRUE
editor_options: 
  chunk_output_type: console
---



# Purpose


The purpose of this script is to conduct the actual parsing of Cochrane reviews. It is assumed that multiple reviews across multiple reviewers are provided.


# Setup

```{r include=FALSE}
knitr::opts_chunk$set(fig.retina = 2)
```

```{r ipsum_setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
#library(hrbrthemes)
library(tidyverse)  # data wrangling
library(rvest)  # web scraping
library(xml2)  # web scraping
library(stringr)  # string manipulation
library(printr)  # print dfs as tables
library(glue)  # glueing
library(rcrossref)  # citation count
#library(conflicted)
library(glue)
library(polite)
library(tidytext)
library(readxl)
library(magrittr)
#update_geom_font_defaults(font_rc)
```


Declare conflict preferences:

```{r}
#conflict_prefer("filter", "dplyr")
```



# List of dois

Provide a list of DOIs (pointing to Cochrane reviews) to be parsed:

```{r}
dois_list <- readxl::read_xlsx("data/doi-list-reviewer.xlsx")
```



## Check
 
Count how many reviews per reviewer are submitted:

```{r}
dois_list %>% 
  count(reviewer)
```


## Replace PF by SJ

```{r}
dois_list2 <-
  dois_list %>% 
  mutate(reviewer = ifelse(reviewer == "PF",
                           "SJ", reviewer))
```



```{r}
dois_list2 %>% 
  count(reviewer)
```


```{r}
write_xlsx(dois_list2, config$dois_file)
```


### Check


```{r}
dois_list3 <- readxl::read_xlsx(config$dois_file)
```

```{r}
dois_list3 %>% 
  count(reviewer)
```


## Subsamples of reviewers

For curiosity, let's look to some particular reviewers:

```{r}
dois_jh <- dois_list %>% 
  filter(reviewer == "JH")

dois_hw <- dois_list %>% 
  filter(reviewer == "HW") %>% 
  pull(url)
```



## Get sample for each reviewer

```{r}
dois_by_reviewer_sample <- 
  dois_list %>% 
  group_by(reviewer) %>% 
  slice(1:50) %>% 
  drop_na()
```


```{r}
dois_by_reviewer_sample %>% 
  count(reviewer)
```



## URLs for checking


For demonstration and testing purposes, here's a list of relevant DOIs:

```{r}
reviews_ss1 <- "http://dx.doi.org/10.1002/14651858.CD001180.pub4"


# mindfulness open access review on intervention:
# friendly review:
mindfulness_url <- "https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD012791.pub2/full"  # 2 sof tables


cochrane_url <- dois_reviews_paywalled[1]

# paywalled url:
paywalled_url <- "https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD013879/full"

# friendly review:
friendly_url <- "http://dx.doi.org/10.1002/14651858.CD003474.pub4"

# no "summary of findings table"
nosumtable_url <- "https://doi.org/10.1002/14651858.CD009326.pub3"


# not recent review:
old_version_url <- "https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD001352/full"


url_throws_error <- "http://dx.doi.org/10.1002/14651858.CD000245.pub4"

url_withdrawn <- "https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD004125.pub3/full"

url_jh1 <- dois_jh[1]

review_url <- prob_url 

url_np <- "https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD012137.pub2/full"

url_404 <- "https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD007701.pub4/full"

bad_url <- "https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD012137.pub2/full"

bad_url2 <- "https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD004123.pub4"

prob_url <- "https://www.cochranelibrary.com/cdsr/doi/10.1002/14651858.CD009099.pub3"
```




# Source functions

```{r}
source("funs/helper-funs.R")
source("funs/funs-parse-cochrane.R")
source("funs/get_summary_table.R")
source("funs/parse-review-parts.R")
```






## Init

Let's define some constants we might need later on.

### Constants 

```{r}
count_reviews <- 1
table_number <- 1
overwrite <- FALSE
verbose <- TRUE
reviewer <- "ss"
overwrite_file <- TRUE
init_new_review()
output_dir <- "output"
file_type = "csv"
```





## Test it

```{r test-parse-review}
test_review <- parse_review(mindfulness_url, 
                            overwrite = TRUE,
                            reviewer = "?",
                            output_dir_to_write = "output")
test_review <- parse_review(bad_url2)
test_review <- parse_review(mindfulness_url, overwrite = TRUE)
```




# Parse reviews


## Loop


### all



```{r}
count_reviews <- 1

reviews_all_50 <- 
  map2_dfr(
    .x = dois_by_reviewer_sample$url,
    .y = dois_by_reviewer_sample$reviewer,
    .f = ~ parse_review(review_url = .x,
                        reviewer = .y,
                        overwrite = TRUE,
                        output_dir = glue("output/{.y}")))


writexl::write_xlsx(reviews_all_50, path = "output/all_reviewers/all_reviewers_50.xlsx")
```


```{r}
reviews_all_50 %>% 
  count(reviewer)
```



#### Read from disk

```{r}
reviews_all_50 <- 
  read_xlsx("output/all_reviewers/all_reviewers_50.xlsx")
```



#### Save in parts (per reviewer)

```{r}

reviewers <- 
reviews_all_50 %>% 
  select(reviewer) %>% 
  distinct(reviewer) %>% 
  pull(reviewer)


reviewers %>% 
  walk( ~ write_csv(
    reviewers_all_50 %>% filter(reviewer == .),
    file = glue("output/all_reviewers/sample_50_{.}.csv")))

```




### JH


```{r}
dois_jh1 <-
  dois_jh %>% 
  slice(80:100) %>% 
  pull(url) 

review_jh1 <- 
  dois_jh1 %>% 
  map_dfr(parse_review, .id = "id_review", output_dir = "output/jh",
          reviewer = "jh",
          overwrite_file = FALSE)
```



```{r}
writexl::write_xlsx(review_jh1, path = "output/reviews_jh1.xlsx")
```


### NP



```{r}
dois_np <- 
  read_csv("data/dois_np.csv")


```


```{r}
reviews_np <- 
  dois_np %>% 
  pull(url) %>% 
  #`[`(6:8) %>% 
  map_dfr(parse_review, 
          .id = "id_review", 
          output_dir = "output/np",
          overwrite_file = TRUE,
          reviewer = "np")


writexl::write_xlsx(reviews_np2, path = "output/np/reviews_np2.xlsx")
```




### HW

```{r}
reviews_parsed_hw <-
  dois_hw %>% 
  magrittr::extract(49:50) %>% 
  map_dfr(parse_review, output_dir = "output/hw")
```

```{r}
reviews_parsed_hw 
```

```{r}
writexl::write_xlsx(reviews_parsed_hw, path = "output/hw/reviews_hw.xlsx")
```



### ss



```{r}
dois_ss <- 
  dois_by_reviewer_sample %>% 
  filter(str_detect(reviewer, "SS")) %>% 
  #slice(5:50) %>% 
  pull(url)

count_reviews <- 1
reviews_ss <- 
  c(bad_url2) %>% 
  map_dfr(parse_review, 
          .id = "id_review", 
          output_dir = "output/ss",
          overwrite_file = TRUE,
          reviewer = "ss")
```



```{r}
writexl::write_xlsx(review_ss, path = "output/ss/reviews_ss.xlsx")
```







```{r}
reviews_parsed4 <- 
   dois_reviews_2017[43:50] %>% 
  # c(nosumtable_url, mindfulness_url, old_version_url) %>% 
   #old_version_url %>% 
   map_dfr(parse_review, .id = "id_review")
```



### ML


```{r}
dois_ml <- 
  dois_list %>% 
  filter(tolower(reviewer) == "ml") %>% 
  #filter(url == "http://dx.doi.org/10.1002/14651858.CD009955.pub3") %>% 
  pull(url)
```



```{r}
count_reviews <- 1
reviews_ml <- 
  dois_ml %>% 
  map_dfr(parse_review, 
          .id = "id_review", 
          output_dir = "output/ML",
          overwrite_file = TRUE,
          reviewer = "ml")
```


```{r}
writexl::write_xlsx(reviews_ml, path = "output/ML/reviews_ml.xlsx")
```


### DK



```{r}
dois_dk <- 
  dois_list %>% 
  filter(tolower(reviewer) == "dk") %>% 
  #filter(url == "http://dx.doi.org/10.1002/14651858.CD009955.pub3") %>% 
  pull(url)
```

```{r}
length(dois_dk)
```





```{r}
count_reviews <- 1
reviews_dk <- 
  dois_dk %>% 
  map_dfr(parse_review, 
          .id = "id_review", 
          output_dir = "output/dk",
          overwrite_file = TRUE,
          reviewer = "dk")
```


```{r}
writexl::write_xlsx(reviews_dk, 
                    path = "output/dk/reviews_output_machine_dk.xlsx")
```


```{r}
reviews_dk %>% 
  write_csv(file = "output/dk/reviews_output_machine_dk.csv")
```



# Convert to data frame


```{r}
reviews_parsed2 <- 
   reviews_parsed %>% 
   mutate(review_id = duplicated(doi)) %>% 
   select(review_id, doi, everything())
```




# Save to disk


```{r}
write_csv(reviews_parsed3, 
            file = paste0("test_reviews_infos3", ".csv"))

writexl::write_xlsx(reviews_parsed3,
                    path = "test_reviews_infos3.xlsx")

writexl::write_xlsx(reviews_ss,
                    path = "output/ss/reviews_machine_ss.xlsx")
write_csv(reviews_ss, 
            file = "output/ss/reviews_ss.csv")

```


